 

### 2019-02-02 Manuscript/SupplementaryMaterial.Rmd
Manuscript update

Following @nunez2011bayesian, the joint density of \(\Theta\) and \(R\) for the
PN distribution equals
\begin{equation}\label{pnreg}
f(\theta,r \mid \boldsymbol{\mu}, \boldsymbol{I}) = \frac{r}{2\pi} \exp\left[- \frac{(r\boldsymbol{u} - \boldsymbol{\mu})^t(r\boldsymbol{u} - \boldsymbol{\mu})}{2}\right],
\end{equation}
\noindent where \(\boldsymbol{u}= \begin{bmatrix} \cos (\theta) \\ \sin (\theta)
\end{bmatrix}\) and $r$ is the same as in \eqref{circlinlink} and
\eqref{ycondtheta} and is defined in \eqref{projection}. In a regression setup
the outcomes \(\theta_i,r_i\) for each individual \(i = 1, \dots, n\), where
\(n\) is the sample size, are generated independently from the distribution with
density \eqref{pnreg}. The mean vector \(\boldsymbol{\mu}_i \in \mathbb{R}^2\)
is then defined as \(\boldsymbol{\mu}_i = \boldsymbol{B}^t\boldsymbol{z}_i\)
where the vector \(\boldsymbol{z}_i\) is a vector of dimension $p + 1$ that
contains the covariate values and the value 1 to estimate an intercept and
\(\boldsymbol{B} = (\boldsymbol{\beta}^{I}, \boldsymbol{\beta}^{II})\) contains
the regression coefficients and intercepts.

@@

Following @wang2012directional and @hernandez2016general the joint density of
\(R\) and \(\Theta\) for the GPN distribution equals
\begin{equation}\label{gpnreg}
f(\theta, r \mid \boldsymbol{\mu}, \boldsymbol{\Sigma}) = \frac{r}{2\pi\tau} \exp\left[ -\frac{(r\boldsymbol{u}-\boldsymbol{\mu})^{t}\boldsymbol{\Sigma}^{-1}(r\boldsymbol{u}-\boldsymbol{\mu})}{2}\right],
\end{equation}
\noindent where we recall that \(\boldsymbol{\Sigma} = \begin{bmatrix} \tau^2 +
\xi^2 & \xi\\ \xi & 1 \end{bmatrix}\). In a regression setup the outcomes
\(\theta_i\) and \(r_i\) for each individual are generated independently from
\eqref{gpnreg}. The mean vector \(\boldsymbol{\mu}_i \in \mathbb{R}^2\) is
defined in the same way via covariates as for the modified CL-PN distribution.

@@

\indent We use the loglikelihoods of the following conditional densities for the
computation of the PLSL in the teacher data:

@@

$y_i \mid \mu_i, \sigma^2 \sim N(\mu_i, \sigma^2)$, where $\mu_i = \hat{y}_i$ and for $\theta_i$ we use \eqref{pnreg}.

@@

$y_i \mid \mu_i, \sigma^2 \sim N(\mu_i, \sigma^2)$, where $\mu_i = \hat{y}_i$ and for $\theta_i$ we use \eqref{gpnreg}.

@@

$y_i \mid \theta_i, \nu_i, \mu_i, \kappa, \alpha \sim W\left(\nu_i(1-\tanh(\kappa)\cos(\theta_i - \mu_i))^{1/\alpha}, \alpha\right)$, a Weibull distribution.

$\theta_i \mid y_i, \nu_i, \mu_i, \kappa, \alpha, \lambda \sim SSVM\left(\mu_i, (\nu_iy_i)^{\alpha}(\tanh{\kappa})\right)$, a sine-skewed von Mises distribution.

\item For the modified joint projected and skew normal model:

@@

where $SSN$ is the skew normal distribution.
\end{itemize}

>>>>

Following @nunez2011bayesian, the joint density of \(\Theta\) and \(R\) for the
PN distribution equals
\begin{equation}\label{pnreg}
f(\theta,r \mid \boldsymbol{\mu}, \boldsymbol{I}) = \frac{1}{2\pi} \exp\{-0.5 \mid\mid\mu^2\mid\mid\}\exp\{-0.5\left[r^2 -2r(u^t\mu) \right]\},
\end{equation}
\noindent where \(\boldsymbol{u}= \begin{bmatrix} \cos (\theta) \\ \sin (\theta)
\end{bmatrix}\) and $r$ is the same as in \eqref{circlinlink} and
\eqref{ycondtheta} and is defined in \eqref{projection}. In a regression setup
the outcomes \(\theta_i,r_i\) for each individual \(i = 1, \dots, n\), where
\(n\) is the sample size, are generated independently from the distribution with
density \eqref{pnreg}. The mean vector \(\boldsymbol{\mu}_i \in \mathbb{R}^2\)
is then defined as \(\boldsymbol{\mu}_i = \boldsymbol{B}^t\boldsymbol{z}_i\)
where the vector \(\boldsymbol{z}_i\) is a vector of dimension $p + 1$ that
contains the covariate values and the value 1 to estimate an intercept and
\(\boldsymbol{B} = (\boldsymbol{\beta}^{I}, \boldsymbol{\beta}^{II})\) contains
the regression coefficients and intercepts.

@@

Following @wang2012directional and @hernandez2016general the joint density of
\(R\) and \(\Theta\) for the GPN distribution equals
\begin{equation}\label{gpnreg}
f(\theta, r \mid \boldsymbol{\mu}, \boldsymbol{\Sigma}) = \frac{r}{2\pi\tau} \exp\left[ -\frac{(r\boldsymbol{u}-\boldsymbol{\mu})^{t}\boldsymbol{\Sigma}^{-1}(r\boldsymbol{u}-\boldsymbol{\mu})}{2\tau^2}\right],
\end{equation}
\noindent where we recall that \(\boldsymbol{\Sigma} = \begin{bmatrix} \tau^2 +
\xi^2 & \xi\\ \xi & 1 \end{bmatrix}\). In a regression setup the outcomes
\(\theta_i\) and \(r_i\) for each individual are generated independently from
\eqref{gpnreg}. The mean vector \(\boldsymbol{\mu}_i \in \mathbb{R}^2\) is
defined in the same way via covariates as for the modified CL-PN distribution.

@@

\indent We use the following loglikelihoods for the
computation of the PLSL in the teacher data:

@@

$$l(y) = \log(1) - \log(\sqrt{2\pi\sigma^2}) + \sum(\hat{y}_i-(\gamma_0 + \gamma_{cos}\cos(\theta_i)r_i +
\gamma_{sin}\sin(\theta_i)r_i + \gamma_1\text{SE}_i))^2/2\sigma^2$$

$$l(\theta) = \log(1) - \log(2\pi) + \sum -0.5\hat{\mu}_i^2 - 0.5(r_i^2 - 2r_iu_i^t\hat{\mu}_i)$$
where $u_i = (cos\theta_i, \sin \theta_i)$ and $\hat{\mu}_i = (\beta_0^{I} + \beta_0^{I}\text{SE}_i, \beta_0^{II} + \beta_0^{II}\text{SE}_i)^t$.

@@

$$l(y) = \log(1) - \log(\sqrt{2\pi\sigma^2}) + \sum(\hat{y}_i-(\gamma_0 + \gamma_{cos}\cos(\theta_i)r_i +
\gamma_{sin}\sin(\theta_i)r_i + \gamma_1\text{SE}_i))^2/2\sigma^2$$

$$l(\theta) =  \log(1) - \log(2\pi+\tau) - \sum \log(r_i) + (u_i^t\hat{\mu}_i\Sigma^{-1}(u_i^t\hat{\mu}_i)^t)/2\tau^2$$
where $u_i = (cos\theta_i, \sin \theta_i)$ and $\hat{\mu}_i = (\beta_0^{I} + \beta_0^{I}\text{SE}_i, \beta_0^{II} + \beta_0^{II}\text{SE}_i)^t$.

@@

$$l(y) = \log\alpha + \sum\log h_i^\alpha + \sum\log y_i^{\alpha - 1} - \sum(h_iy_i)^\alpha$$

where $h_i = \exp\{\hat{y}_i\}\{1-\tanh(\kappa)\cos(\theta_i - \hat{\theta}_i)\}^{1/\alpha}$, $\hat{y}_i = \gamma_0 + \gamma_1\text{SE}_i$ and $\hat{\theta}_i = \beta_0 +  2\tan^{-1}(\beta_1\text{SE}_i))$ .

$$l(\theta) = \log(1) - \sum\log 2\pi I_0(c_i) + \sum\log\{1 + \lambda \sin(\theta_i - \hat{\theta}_i\} + \sum c_i\cos(\theta_i - \hat{\theta}_i)$$

where $c_i = y_i^{\alpha}\exp(\hat{y}_i)^{\alpha}\tanh\kappa$, and $I_{0}$ is a Bessel function of order $0$.

\item For the modified joint projected and skew normal model we take the loglikelihoods of the following distributions:

@@

where $SSN$ is the skew normal distribution. Computationally this comes down to taking the log of the density values for a univariate and multivariate normal distribution (with mean and variance specified as above) for the linear and circular outcome respectively.

### 2019-02-02 Manuscript/SupplementaryMaterial.tex
Manuscript update

Following Nuñez-Antonio, Gutiérrez-Peña, \& Escarela (2011), the joint
density of \(\Theta\) and \(R\) for the PN distribution equals
\begin{equation}\label{pnreg}
f(\theta,r \mid \boldsymbol{\mu}, \boldsymbol{I}) = \frac{r}{2\pi} \exp\left[- \frac{(r\boldsymbol{u} - \boldsymbol{\mu})^t(r\boldsymbol{u} - \boldsymbol{\mu})}{2}\right],
\end{equation} \noindent where
\(\boldsymbol{u}= \begin{bmatrix} \cos (\theta) \\ \sin (\theta) \end{bmatrix}\)
and \(r\) is the same as in \eqref{circlinlink} and \eqref{ycondtheta}
and is defined in \eqref{projection}. In a regression setup the outcomes
\(\theta_i,r_i\) for each individual \(i = 1, \dots, n\), where \(n\) is
the sample size, are generated independently from the distribution with
density \eqref{pnreg}. The mean vector
\(\boldsymbol{\mu}_i \in \mathbb{R}^2\) is then defined as
\(\boldsymbol{\mu}_i = \boldsymbol{B}^t\boldsymbol{z}_i\) where the
vector \(\boldsymbol{z}_i\) is a vector of dimension \(p + 1\) that
contains the covariate values and the value 1 to estimate an intercept
and
\(\boldsymbol{B} = (\boldsymbol{\beta}^{I}, \boldsymbol{\beta}^{II})\)
contains the regression coefficients and intercepts.

@@

Following Wang \& Gelfand (2013) and Hernandez-Stumpfhauser et al.
(2016) the joint density of \(R\) and \(\Theta\) for the GPN
distribution equals \begin{equation}\label{gpnreg}
f(\theta, r \mid \boldsymbol{\mu}, \boldsymbol{\Sigma}) = \frac{r}{2\pi\tau} \exp\left[ -\frac{(r\boldsymbol{u}-\boldsymbol{\mu})^{t}\boldsymbol{\Sigma}^{-1}(r\boldsymbol{u}-\boldsymbol{\mu})}{2}\right],
\end{equation} \noindent where we recall that
\(\boldsymbol{\Sigma} = \begin{bmatrix} \tau^2 + \xi^2 & \xi\\ \xi & 1 \end{bmatrix}\).
In a regression setup the outcomes \(\theta_i\) and \(r_i\) for each
individual are generated independently from \eqref{gpnreg}. The mean
vector \(\boldsymbol{\mu}_i \in \mathbb{R}^2\) is defined in the same
way via covariates as for the modified CL-PN distribution.

>>>>

Following Nuñez-Antonio, Gutiérrez-Peña, \& Escarela (2011), the joint
density of \(\Theta\) and \(R\) for the PN distribution equals
\begin{equation}\label{pnreg}
f(\theta,r \mid \boldsymbol{\mu}, \boldsymbol{I}) = \frac{1}{2\pi} \exp\{-0.5 \mid\mid\mu^2\mid\mid\}\exp\{-0.5\left[r^2 -2r(u^t\mu) \right]\},
\end{equation} \noindent where
\(\boldsymbol{u}= \begin{bmatrix} \cos (\theta) \\ \sin (\theta) \end{bmatrix}\)
and \(r\) is the same as in \eqref{circlinlink} and \eqref{ycondtheta}
and is defined in \eqref{projection}. In a regression setup the outcomes
\(\theta_i,r_i\) for each individual \(i = 1, \dots, n\), where \(n\) is
the sample size, are generated independently from the distribution with
density \eqref{pnreg}. The mean vector
\(\boldsymbol{\mu}_i \in \mathbb{R}^2\) is then defined as
\(\boldsymbol{\mu}_i = \boldsymbol{B}^t\boldsymbol{z}_i\) where the
vector \(\boldsymbol{z}_i\) is a vector of dimension \(p + 1\) that
contains the covariate values and the value 1 to estimate an intercept
and
\(\boldsymbol{B} = (\boldsymbol{\beta}^{I}, \boldsymbol{\beta}^{II})\)
contains the regression coefficients and intercepts.

@@

Following Wang \& Gelfand (2013) and Hernandez-Stumpfhauser et al.
(2016) the joint density of \(R\) and \(\Theta\) for the GPN
distribution equals \begin{equation}\label{gpnreg}
f(\theta, r \mid \boldsymbol{\mu}, \boldsymbol{\Sigma}) = \frac{r}{2\pi\tau} \exp\left[ -\frac{(r\boldsymbol{u}-\boldsymbol{\mu})^{t}\boldsymbol{\Sigma}^{-1}(r\boldsymbol{u}-\boldsymbol{\mu})}{2\tau^2}\right],
\end{equation} \noindent where we recall that
\(\boldsymbol{\Sigma} = \begin{bmatrix} \tau^2 + \xi^2 & \xi\\ \xi & 1 \end{bmatrix}\).
In a regression setup the outcomes \(\theta_i\) and \(r_i\) for each
individual are generated independently from \eqref{gpnreg}. The mean
vector \(\boldsymbol{\mu}_i \in \mathbb{R}^2\) is defined in the same
way via covariates as for the modified CL-PN distribution.
